Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-09 manuscript/manuscript.Rmd
msy, etc

There are several strategies that have been used to manage fisheries: *escapement*, *maximum sustainable yield (MSY)*, *total allowable catch (TAC)*, among others.
We collectively refere to these as *classical*, and will compare their performance to RL-based management strategies.
As shown in Fig. \ref{fig:tbd}, classical strategies have the common aspect of reducing the complex dynamics of the fishery ecosystem to a single equation governing the harvested population (say, $F$). 
A common example is using a logistic growth equation,
$$
  F_{t+1} - F_t = r F_t( 1 - F_t / K),
$$
where the interaction between $F$ and its environment is summarized to two parameters, the growth rate $r$, and the carrying capacity $K$.

>>>>

There are several strategies that have been used to manage fisheries: *escapement*, *maximum sustainable yield (MSY)*, *total allowable catch (TAC)*, among others.
We collectively refere to these as *classical*, and will compare their performance to RL-based management strategies.
As shown in Fig. \ref{fig:tbd}, classical strategies have the common aspect of reducing the complex dynamics of the fishery ecosystem to a single equation governing the harvested population (say, $F$). 
A common example is using a logistic growth equation,
$$
  F_{t+1} - F_t = r F_t( 1 - F_t / K) - h_t =: L(F_t) - h_t,
$$
where the interaction between $F$ and its environment is summarized to two parameters, the growth rate $r$, and the carrying capacity $K$.
In the equation above, $h_t$ is the *harvest* at timestep $t$.
The goal is to choose the harvest policy $h:F_t\mapsto h_t$ such that long-term profits are maximized.

An advantage of one dimensional approaches is that the optimal policy is often known exactly, and, moreover, is intuitive.
For example, in the logistic equation pointed out above, the maximal sustainable yield of the system is attained at $F = F_{MSY} := K/2$.
The optimizer is an *escapement* policy:
$$
  h_t = \begin{cases}
    F_t - K/2, \qquad &\text{if, } F_t > K/2\\
    0, \qquad &\text{else.}
  \end{cases}
$$
This corresponds to keeping the system at its optimal growth rate as much as possible.

Escapement policies, or more generally *bang bang* policies, tend to be the optimal solution for these types of control problems.
A drawback of these solutions, in the fishery context, is the presence of several timesteps with zero harvest which can arise.
To mend this, certain suboptimal solutions have been constructed for fishery management.

One ubiquitous solution is simply called maximum sustainable yield (MSY).
It consists on letting $h(F) = rF/2$, so that
$$
  h(F_{MSY}) = L(F_{MSY}) = r K/4.
$$
That is, at the MSY biomass, the logistic growth of $F$ is cancelled exactly by the harvest.

The MSY rule fixes the drawback in the escapement policy by having $h(F)>0$ for all $F>0$.
